### 2018-11-06 VM524/HW3/submission.tex
Q2 done

@@

\section{Exercise 2}

\end{document}

>>>>

	where
 	\frac{\bar{D}}{\bar{D}t} = \frac{\partial}{\partial t} + U_k \frac{\partial}{\partial x_k}

@@

\section{Exercise 2}
	The governing equation for the passive scalar $\phi$ is
	\begin{equation}\label{eq:passive}
		\frac{D \phi}{D t} = \Gamma \triangledown^2 \phi
	\end{equation}
	The gradient of (\ref{eq:passive}) is
	\begin{equation}
		\frac{\partial \triangledown \phi}{\partial t} + \triangledown(\vec{U}\cdot\triangledown\phi) = \Gamma \triangledown^2(\triangledown\phi)
	\end{equation}
	An vector operation identity is used
	\begin{equation}
		\triangledown(\vec{f}\cdot\vec{g}) = (\vec{g}\cdot\triangledown)\vec{f} + \vec{g} \times (\triangledown \times \vec{f}) + (\vec{f} \cdot \triangledown)\vec{g} + \vec{f} \times (\triangledown \times \vec{g})
	\end{equation}
	Thus
	\begin{equation}
		\begin{aligned}
			\triangledown(\vec{U} \cdot \triangledown\phi) 
			& = (\triangledown\phi \cdot \vec{U})\vec{U} + \triangledown\phi \times (\triangledown \times \vec{U}) + (\vec{U} \cdot \triangledown) \triangledown \phi + \vec{U} \times (\triangledown \times \triangledown\phi)\\
			& = (\triangledown\phi \cdot \vec{U})\vec{U} + \triangledown\phi \times (\triangledown \times \vec{U}) + (\vec{U} \cdot \triangledown) \triangledown \phi
		\end{aligned}
	\end{equation}
	Hence, the governing equation for $\triangledown\phi$ is
	\begin{equation}\label{eq:gp}
		\frac{D}{Dt}\triangledown\phi = -(\vec{U} \cdot \triangledown\phi)\vec{U} - \triangledown\phi \times (\triangledown \times \vec{U}) + \Gamma \triangledown^2(\triangledown\phi)  
	\end{equation}
	Denote $\vec{W} = \triangledown \phi$, then (\ref{eq:gp}) can be re-written as
	\begin{equation}
		\frac{D}{Dt} \vec{W} = -(\vec{U} \cdot \vec{W})\vec{U} - \vec{W} \times (\triangledown \times \vec{U}) + \Gamma \triangledown^2 \vec{W} \triangleq RHS
	\end{equation}
	Inner product with $\vec{W}$, the 2nd term in $RHS$ vanishes, remaining parts yields
	\begin{equation}
		\frac{D}{Dt} \big(\frac{1}{2}|\vec{W}|^2\big) = -(\vec{U} \cdot \vec{W})^2  + \Gamma \vec{W} \triangledown^2 \vec{W}
	\end{equation}
	since
	\begin{equation}
			\vec{W} \triangledown^2 \vec{W} = \triangledown^2 \big(\frac{1}{2}|\vec{W}|^2\big) - \triangledown \vec{W} : \triangledown \vec{W}
	\end{equation}
	then, the governing equation for the scalar gradient energy $\triangledown\phi \cdot \triangledown\phi$ is
	\begin{equation}
		\frac{D}{Dt} \big(\frac{1}{2}|\vec{W}|^2\big) = -(\vec{U} \cdot \vec{W})^2  + \Gamma \Bigg(\triangledown^2 \big(\frac{1}{2}|\vec{W}|^2\big) - \triangledown \vec{W} : \triangledown \vec{W}\Bigg)
	\end{equation}
	Characteristic scales of dissipation term is estimated as
	\begin{equation}
		\Gamma \triangledown^2(\frac{1}{2} |\vec{W}|^2) \sim \Gamma \frac{\phi^2}{L^4}
	\end{equation}
\end{document}
